Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-03 popl24/hyperprop.tex
checkpoint

\subsection{Passive Security and the Real/Ideal Model} \dnote{would shortening the background info on how simulator model works be a bad idea?} Here we
briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{XXX}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

\subsection{Probabilistic Noninterference}
\label{section-ni}
Previous work has noted
relations between probabilistic noninterference and security
properties such as memory trace obliviousness \cite{XXX} and passive
security \cite{XXX}. And above (Section \ref{section-pmf-examples}) we
have demonstrated that our basic encryption scheme enjoys a noninterference
property. To formulate probabilistic noninterference in
our setting we begin by defining low equivalence of memories.
\begin{definition}[Memory Low Equivalence]
  Given $\store^1$ and $\store^2$ with $\dom(\store^1) = \dom(\store^2) = X$,
  we write $\store^1 =_C \store^2$ iff $\store^1_{X_C} = \store^2_{X_C}$.
\end{definition}
Now, we can define probabilistic noninterference as a property of
programs ensuring that low-equivalent initial memories produce
the same low-observable trace (i.e., corrupt views) \emph{with the
same probability}. 
\begin{definition}[Probabilistic Noninterference]
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, we say that
  $\prog$ satisfies \emph{probabilistic noninterference} iff for all
  $\store_1, \store_2 \in \mems(S)$:
  $$\store_1 =_C \store_2 \implies
    \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}$$
\end{definition}

>>>>

\subsection{Passive Security and the Real/Ideal Model}
\label{section-hyperprop-passive}
Here we briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{XXX}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

\subsection{Probabilistic Noninterference}
\label{section-hyperprop-ni}
Previous work has noted
relations between probabilistic noninterference and security
properties such as memory trace obliviousness \cite{XXX} and passive
security \cite{XXX}. And above (Section \ref{section-pmf-examples}) we
have demonstrated that our basic encryption scheme enjoys a noninterference
property. To formulate probabilistic noninterference in
our setting we begin by defining low equivalence of memories.
\begin{definition}[Memory Low Equivalence]
  Given $\store^1$ and $\store^2$ with $\dom(\store^1) = \dom(\store^2) = X$,
  we write $\store^1 =_C \store^2$ iff $\store^1_{X_C} = \store^2_{X_C}$.
\end{definition}
Now, we can define probabilistic noninterference as a property of
programs ensuring that low-equivalent initial memories produce
the same low-observable trace (i.e., corrupt views) \emph{with the
same probability}. 
\begin{definition}[Probabilistic Noninterference]
  Given a program $\prog$ with $\iov(\prog) = (S,V)$, we say that
  $\prog$ satisfies \emph{probabilistic noninterference} iff for all
  $\store_1, \store_2 \in \mems(S)$:
  $$\store_1 =_C \store_2 \implies
    \margd{(\condd{\progd(\prog)}{\store_1})}{V_C} =
    \margd{(\condd{\progd(\prog)}{\store_2})}{V_C}$$
\end{definition}

### 2023-07-03 popl24/intro.tex
checkpoint

>>>>

Secure Multi-Party Computation (MPC) protocols support data privacy in
important distributed applications such as privacy-preserving machine
learning and Zero-Knowledge proofs in blockchains. MPC methods have
been developed by the cryptography community for many years, while
receiving the attention of the programming languages community only
relatively recently. In contrast, information flow security has
received significant attention in PL theory and practice especially
since the turn of the century \cite{1159651}, including a menagerie of
variants, enforcement mechanisms, and programming frameworks. Much of
this has been enabled by the unified metatheory of
\emph{hyperproperties} \cite{10.5555/1891823.1891830} that establishes
a common conceptual framework for reasoning about and implementing
systems with information flow security.

Our goal is to explore and establish connections between the security
model of MPC-- the \emph{real/ideal} aka \emph{simulator security}
model -- and trace-based hyperproperties, and to leverage these
connections to obtain automated enforcement mechanisms for MPC
protocol development. Currently, proof methods for MPC protocol
development are well-studied \cite{Lindell2017} but manual and 
thus tedious and error-prone, and are also non-standardized and
unfamiliar to most PL theorists. Therefore our exploration will
make both theoretical and practical contributions by bridging a gap between
information flow and simulator security methodologies.

\subsection{The Analysis Challenge of MPC} MPC protocols involve communication
between a group of distributed participants called a \emph{federation}
that collaboratively compute and publish the result of some known
\emph{ideal functionality} $\idealf$, while keeping each party's input
``secret'', without the use of a trusted third party. This last part
is critical. For example, if we take $\idealf$ to be the majority vote
function, a protocol for computing $\idealf$ is MPC-secure if, given
any set of input votes, it correctly computes and publishes the voting
result without directly revealing the votes of individual participants
to the public or to other participants. However, note that by
publishing the output, some information about individual votes may be
implicitly declassified.  For example, in the case of a majority vote
in a federation of size 3, if the motion carries and party 1 has voted
no, then party 1 knows exactly the votes of parties 2 and 3. This
cannot be avoided due to the nature of $\idealf$.

Security in the MPC setting thus means that protocols cannot reveal
any more information than the output of the ideal functionality, which
will be published. The security model also assumes that some subset of
participants can be corrupted and collude adversarially to infer
secret information. The accepted method of demonstrating protocol
security in this setting is to define a \emph{simulation} algorithm
that runs in the ``ideal'' world which, given just the inputs of
corrupted parties and the output of the ideal functionality, is able
to reconstruct information that corrupted parties receive in their
so-called \emph{views} of the protocol running in the real world.
This implies that adversarial views provide no information beyond what
is provided by the ideal output alone. Simulation is defined
probabilistically since MPC protocols typically rely on cryptographic
and probabilistic methods.

In Section \ref{section-hyperprop-passive} we formalize real/ideal
security, and we define and discuss simple examples of MPC protocols
in Section \ref{section-minicat-examples} and more complex ones in
Section \ref{section-composition}. But an immediate and main point in
relation to security hyperproperties is that, due to the potential for
information release in MPC, simulator security is \emph{not} a strict
probabilistic noninterference or trace obliviousness property, as we
show in Section \ref{section-hyperprop-ni}- rather, the public output
allows and sets an upper bound on declassification.

\subsection{Related Work}

We distinguish between \emph{extensional} vs.~\emph{intensional}
properties and analysis of MPC protocols. By extensional, we mean
analysis concerned with the use and interaction of complete protocols
that are proved to be secure. By intensional, we mean analysis of the
inner workings of protocols themselves.

\subsection{Contributions}
